Exploring the tree of numerical semigroups

### 2014-09-22 Papier/article.tex
Fix a mistake on Acknowledgment

\textbf{Acknowledgment.} We would like to thank Shalom Eliahou for his presentation of the tree of numerical semigroups and for the great full discussions on the subject.

>>>>

\textbf{Acknowledgment.} We would like to thank Shalom Eliahou for his presentation of the tree of numerical semigroups and for the interesting discussions on the subject.
